% !TEX program = xelatex
% This is my resume
% by ice1000

\documentclass{resume}

% \usepackage{lastpage}
% \usepackage{fancyhdr}
\usepackage{linespacing_fix} % disable extra space before next section

\begin{document}
% \pagestyle{fancy}
% \fancyhf{}
% \renewcommand\headrulewidth{0pt}
% \cfoot{\thepage\ of \pageref{LastPage}}

\name{Tesla Ice Zhang}

\basicInfo{
  \email{ice1000kotlin@foxmail.com} \textperiodcentered\
  \phone{(+86) 180-8192-5082} \textperiodcentered\
  \github[ice1000]{https://github.com/ice1000} \textperiodcentered\
  \homepage{https://ice1000.org}
  % \linkedin[user]{https://www.linkedin.com/in/user}
}

\section{Education}
\datedsubsection{\textbf{The Pennsylvania State University (PSU)}, PA, US}{08/18 -- Current}
  Major: Computer Science, Anticipated Graduation Date: 06/22, GPA 3.25/4.00

\section{Work Experience}
\datedsubsection{\textbf{Sourcebrella Inc.}, Shenzhen, China}{02/18 -- 07/18}
\role{Intern}{Compiler Front-End, IDE Plugin Development}
\begin{itemize}
  \item Created IntelliJ/CLion/Eclipse plugin of the Pinpoint analyzer. Helped create SonarQube plugin.
  \item Created a multi-threading cross Java/Kotlin source code indexer which index Hadoop in 4 minutes.
  % \item Learned a lot about Linux programming and Clang/LLVM.
\end{itemize}

\datedsubsection{\textbf{PingCAP}, Remote}{08/18 -- Current}
\role{Intern}{TiKV - Ecosystem Team}
\begin{itemize}
  \item Improved many TiKV-relevant libraries, like
    optimizing performance of
    \href{https://docs.rs/crate/grpcio} {grpcio},
    adding new features to
    \href{https://docs.rs/crate/procinfo} {procinfo}.
  \item Helped migrating the Protocal-Buffer library used by TiKV and its Raft implementation.
  % \item Learned a lot about Rust programming, distributed system and databases.
\end{itemize}

\section{Personal Projects}
% \datedsubsection{\textbf{FriceEngine}}{\url{https://icela.github.io/}}
% % \role{Kotlin, C\#, Racket, Ruby}{Founder and main contributer to the Kotlin/C\#/Ruby version}
% A multilingual, natively-written, easy-to-use game engine series.
% \begin{itemize}
%   \item Based on life cycle / utility APIs, based on each languages' built-in GUI framework,
%     easy to install.
%   \item GitHub issues / milestones are used as task / version managing tools, nice changelogs.
%   \item A JavaFX-based drag-and-drop GUI designer, generates multilingual codes for each language.
% \end{itemize}

% \datedsubsection{\textbf{DevKt}}{\url{https://github.com/ice1000/dev-kt}}
% Cross-platform lightweight code editor / Kotlin IDE
% \begin{itemize}
  % \item Built-in Java/Kotlin highlights and completion, that can support other languages
    % via plugins (transplantable from JetBrains IDE's).
    % Has extra build \& run support for Kotlin.
  % \item Flexible architecture, decoupled high-level logic with UI, migration to other UI frameworks is easy.
  % \item Provides fine-grained highlight color and keymap settings, supports hot reload.
% \end{itemize}

\datedsubsection{\textbf{Voile}}{\url{https://github.com/owo-lang/voile-rs}}
Experimental dependently-typed programming language with first-class cases and row-polymorphism
\begin{itemize}
  \item Supports dependent types, meta variable unifications, and non-dependent row-polymorphic Records and Sums.
  \item Implements CLI parser / source code parser and interactive REPL with the help of Rust language's ecosystem.
\end{itemize}

% \datedsubsection{\textbf{minitt-rs}}{\url{https://github.com/owo-lang/minitt-rs}}
% Experimental dependently-typed programming language, based on \href{http://www.cse.chalmers.se/~bengt/papers/GKminiTT.pdf} {Mini-TT}
% \begin{itemize}
  % \item Supports $\Pi$ types (return type depends on input value), $\Sigma$ types (tuple's members' type depend on members' values), sum types and case-split.
  % \item Extendes the type system with subtyping on first-class sum types while still supports recursive types.
  % \item Implements CLI parser / source code parser and interactive REPL with the help of Rust language's ecosystem.
% \end{itemize}

% \datedsubsection{\textbf{Lice language}}{\url{https://github.com/lice-lang/lice}}
% \role{Kotlin, Java}{Founder and main contributer}
% Scalable programming language running on JVM
% \begin{itemize}
  % \item Supports lambda with and lazy (call by need)/macro (call by name)/strict (call by value).
  % \item About 1/20 of Java's (Hotspot 8u151) performance, provides Java interaction and script engine support.
  % \item Provides CLI REPL with GHCi-style code completion/colored output and JetBrains.
    % IDE plugin supporting semantic-based highlights, completion, go-to-definition, rename, eval-and-replace, quick fixes, etc.
% \end{itemize}

\datedsubsection{\textbf{Julia-IntelliJ}}{\url{https://github.com/JuliaEditorSupport/julia-intellij}}
Julia plugin for JetBrains IDEs
\begin{itemize}
  \item Semantic-based highlighting, quick fixes, completion, parameter hint, special input mode for Unicode characters.
  \item Use Markdown plugin to highlight doc strings, provides REPL and SciView (showing the output of Plot libraries).
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

%% \section{\faHeartO\ Achievements}
%% \datedline{}{Aug. 2017}

\section{Skills}
\begin{itemize}[parsep=0.25ex]
  \item \textbf{Programming Languages}:
    \textbf{multilingual} (not limited to any specific language),
    and especially experienced in Java/Kotlin/Rust/C\#/Agda/Haskell,
    comfortable with Dart/C/C++/F\#/F$\star$/Idris/Perl (in random order).

  % compiler theories
  \item \textbf{Compilers}:
    understand various program representations such as Control Flow Graphs
    and A-Normal Form.

  % language Kotlin
  \item \textbf{Kotlin/Java}:
    \textbf{3 years} of experience,
    \textbf{4} projects collected in
    \href{https://kotlin.link/?q=ice} {Awesome Kotlin},
    familiar with JNI, Gradle, and Swing, have
    experience in using the Kotlin compiler as code analyze tool.

  \item \textbf{Type System}:
    understand dependent types / (co)algebra Martin-L\"{o}f Type Theory,
    currently studying Cubical Type Theory,
    familiar with Idris, Agda (\textbf{1 years} of experience, contributor) and F$\star$
    \subitem Source code studied: Agda, Idris, MiniAgda, Mini-TT and TOG.

  \item \textbf{JetBrains MPS}:
    understand concepts and applications of \textbf{Language-Oriented Programming}.

  \item \textbf{IDE Toolings}:
    \textbf{2 years} of experience,
    familiar with the IntelliJ Platform infrastructure and overall
    architecture (created the
    \href{https://plugins.jetbrains.com/plugin/10413}
         {Julia plugin},
    \href{https://plugins.jetbrains.com/plugin/12176}
         {Dependently-Typed Lambda Calculus plugin},
    \href{https://plugins.jetbrains.com/plugin/12046}
         {Pest plugin} and many others), also have experience with Eclipse/SonarQube

  % platforms I am familiar with
  \item \textbf{Mobile Development}:
    \textbf{2 years} of experience,
    Android (Java, Kotlin (Anko)), Fuchsia (Flutter).

  \item \textbf{Developing Tools}:
    can adapt to any editors/OSs, usually use JetBrains IDEs and Emacs under Ubuntu,
    have experience with team tools like YouTrack, Jira, GitHub, BitBucket, Coding.net, Tower.
\end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
% \datedline{Other awards}{2015}

\section{Miscellaneous}
\begin{itemize}[parsep=0.25ex]
  \item Literate Agda Blog: \url{https://ice1000.org/lagda/}, using Literate mode of Agda improved by me
  \item Bintray: \url{https://bintray.com/ice1000}, published some useful JVM libraries
  \item Crates.io: \url{https://crates.io/users/ice1000}, published some interesting Rust libraries
  \item IntelliJ Plugin developer: \url{https://plugins.jetbrains.com/author/10a216dd-c558-4aaf-aa8a-723f431452fb}
  %% \item Books about formal verification I've written: \url{https://github.com/ice1000/Books}
  \item Languages: English - fluent (TOEFL 100), Chinese - native speaker
  %% \item Opensource contributions: \url{https://ice1000.org/opensource-contributions/} \\
  %%   pull-requested (functional improvements) to organizations like \textit{Microsoft, JetBrains, Ruby, Dropbox, PingCAP, TiKV},
  %%   projects like \textit{agda, imgui, shields.io, intellij-solidity, IntelliJ-EmmyLua, intellij-haskell}
  \item Opensource Contributions: \url{https://ice1000.org/opensource-contributions/}
    % member of \textsf{JuliaEditorSupport}, \textsf{agda}, \textsf{pest-parser}, \textsf{EmmyLua} and more,
    % contributed to \textsf{KaTeX, shields.io, djinni, raft-rs, grpc-rs, intellij-solidity, intellij-haskell, intellij-rust}
    % and more (apart from organization projects)
  \item StackOverflow: \url{https://tinyurl.com/y5cmw3dz},
    3000+ reputations, also active on \href{https://stackexchange.com/users/9532102/} {other StackExchange sites}
  % https://raw.githubusercontent.com/ice1000/resume/master/resume.pdf
  \item Get the latest version of this resume: \url{https://tinyurl.com/y8xdlfug}
  \item \textbf{1 dan} on
    \href{https://www.codewars.com/users/ice1000} {CodeWars},
    ranked \#32 on the whole site, primarily in Haskell, Agda and Idris
  \item Love making friends
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}

